---
title: "Preprocess",
author: "Luuc van der Zee",
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##"
)
```

```{r, echo = FALSE}
library(DBI)
library(RSQLite)
library(tidyverse)
```

First, load the data from the database:

```{r}
db_path <- "../js/genius/db/data.db"
con <- dbConnect(RSQLite::SQLite(), db_path)
table_name <- "songs"
songs <- dbReadTable(con, table_name)
dbDisconnect(con)

songs_tbl <- as_tibble(songs)
```

## Removing missing lyrics

Turns out there are also a few lyrics missing. We will remove those too:

```{r}
songs_tbl <- songs_tbl %>%
  filter(!is.na(lyrics))
```

## Removing short lyrics

Some songs (mainly skits) have very short lyrics. We will remove those too:

```{r}
songs_tbl <- songs_tbl %>%
  mutate(length = nchar(lyrics)) %>%
  filter(length > 133) %>%
  select(id, artist, url, lyrics, date) %>%
  rename(year = date)
```

## Removing duplicate songs

```{r}
songs_tbl <- songs_tbl %>% distinct(url, .keep_all = TRUE)
```

## Remove French and German artists

```{r}
foreign_language_artists <- c(
  "Casper",
  "Manau"
)

songs_tbl <- songs_tbl %>% 
  filter(!(artist %in% foreign_language_artists))
```

## For some reason, one song seems to be form the year 1901. Fix this

```{r}
songs_tbl <- songs_tbl %>% mutate(year = replace(year, year == 1901, 2010))
```

## Output

Finally, we will save the resulting cleaned data to csv:

```{r}
write_csv(songs_tbl, "./songs.csv")
```