---
title: "Topic analysis",
author: "Luuc van der Zee",
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##"
)
```

```{r, echo = FALSE}
library("quanteda", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
library(tidyverse)
library(topicmodels)
library(knitr)
library(readxl)
```

## Data loading

```{r}
songs <- read_csv("./songs.csv")

songs_dfm <- songs %>%
  select(id, lyrics) %>%
  corpus(docid_field = "id", text_field="lyrics") %>%
  dfm(remove = stopwords("en"), remove_punct = T, remove_numbers = T) %>%
  dfm_trim(min_termfreq = 2)
```

## Running the topic model

```{r}
number_of_topics <- 30

songs_lda_model <- LDA(
  songs_dfm,
  k = number_of_topics,
  method = "Gibbs",
  control = list(verbose=0L, seed = 123, burnin = 100, iter = 500)
)
```

## Coming up with topic names

First, we will view the first 10 words of each topic. Second, we will get the 5 songs that have the highest probability for that particular topic, which we will refer to as the most 'representative'. Based on the terms and the most representative songs, we will then pick a name for each topic.

```{r}
song_topic_probability_matrix <- songs_lda_model@gamma

get_most_representative_songs <- function(topic_number, number_of_songs = 5) {
  topic_probability_vector <- song_topic_probability_matrix[, topic_number] %>% as.vector()
  indices_most_representative_songs <- order(topic_probability_vector, decreasing = TRUE)[1:number_of_songs] 
  
  return(songs$url[indices_most_representative_songs])
}

strip_url <- function(url) {
  result <- url %>% substr(nchar("https://genius.com/")  + 1, nchar(url) - nchar('-lyrics'))
  return(result)
}

songs_per_topic <- matrix(
  1:number_of_topics %>%
    sapply(get_most_representative_songs) %>%
    sapply(strip_url),
  ncol = 30
)

topic_names <- c(
  "1. Making love",
  "2. Words ending in -ing",
  "3. Working it/starting fights",
  "4. Rapping (1)",
  "5. Today/tonight",
  "6. Getting high",
  "7. Past tense",
  "8. Let's go/La la la",
  "9. Money",
  "10. Race and police",
  "11. Miscellaneous (1)",
  "12. Miscellaneous (2)",
  "13. Trap vernacular",
  "14. Miscellaneous (3)",
  "15. Love problems",
  "16. Creole clubbing",
  "17. Filler words",
  "18. Religion and space",
  "19. Miscellaneous (4)",
  "20. N-word",
  "21. Foreign languages",
  "22. Miscellaneous (5)",
  "23. Life and nature",
  "24. Miscellaneous (6)",
  "25. The urban",
  "26. Counting",
  "27. Shaking it",
  "28. Violence",
  "29. Rapping (2)",
  "30. Sex-related swearing"
)
```


## Validating topic coherence (word intrusion)

First, we will create a word intrusion test as follows:

```{r}
terms_per_topic <- get_terms(songs_lda_model, 10)

set.seed(123)

intruders <- sample(songs_dfm@Dimnames$features, number_of_topics)
terms_with_intrusion <- matrix(1:number_of_topics %>% sapply(function(i) {
  row <- c(
    terms_per_topic[1:5, i],
    intruders[i]
  )

  return(sample(row))
}), ncol = 6, nrow = 30, byrow = T)

write_csv(terms_with_intrusion %>% as_tibble(), './word_intrusion/word-intrusion-test.csv', col_names = FALSE)
```

We now load in the answers that people gave to the intrusion test so that we can measure topic coherence:

```{r}
all_answers <- read_excel("./word_intrusion/answers-test.xlsx") %>%
  select(-QUESTION)

number_of_respondents <- ncol(all_answers)

get_topic_coherence <- function(topic_number) {
  intruder <- intruders[topic_number]
  answers <- all_answers[topic_number, ]
  
  return(sum(answers == intruder) / number_of_respondents) 
}

coherence_per_topic <- 1:30 %>% sapply(get_topic_coherence)
mean_coherence <- mean(coherence_per_topic)
baseline_coherence <- 1 / 6

ggplot(tibble(topic = 1:30 %>% as.factor(), coherence = coherence_per_topic), aes(x = topic, y = coherence)) +
  geom_col() +
  geom_hline(yintercept = mean_coherence, color = "blue") +
  geom_hline(yintercept = baseline_coherence, color = "red")
```

## Creating topic tables

```{r}
# This part was used to create the tables in the `./topics` folder
colnames(terms_per_topic) <- topic_names
colnames(songs_per_topic) <- topic_names

# kable(songs_per_topic[, 1:5], format = "markdown", longtable = TRUE)
```

## Plotting topics over time

```{r}
plot_topic_over_time <- function(topic_number) {
  topic_probability_vector <- song_topic_probability_matrix[, topic_number] %>% as.vector()
  topic_tbl <- tibble(
    year = songs$year,
    topic_probability = topic_probability_vector
  )
  
  mean_probability_per_year <- topic_tbl %>%
    group_by(year) %>%
    summarize(mean_probability = mean(topic_probability))
  
  ggplot(
    mean_probability_per_year,
    aes(x = year, y = mean_probability)
  ) +
    geom_line() +
    geom_point()
}

# plot_topic_over_time(30)
```

